Pool Model

### 2023-12-20 pool_model.tex
comment out many citations; specify that we track volume and total amount of nutrients/inhibitor

- \cite{emonet_agentcell_2005, gorochowski_bsim_2012, li_nufeb_2019, kreft_bacsim_1998}: examples of another toolboxes for bacterial communities modeling (ABM).\\
More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.
In general, bacterial communities in 2D can experience collective motion called swarming~\cite{wu_collective_2015}.
Some works modelled 2D motile bacteria:
    \item \cite{decoene_microscopic_2011}: 2D chemotactic self-propelled bacterial motion of the flagellated bacteria (e.g. E. coli, B. subtilis).
    Chemotaxis here was driven by the oxygen concentrations.
    \item \cite{rosser_modelling_2014}: modeling of the bacterial reorintation, rotation.
    \item \cite{sokolov_physical_2012, li_amplified_2008}: modeling of the bacteria using hydrodynamic interactions and Brownian motion.
    Fluctuations in velocity and rotations.
    (\cite{li_amplified_2008}: Brownian motion gives right motion observed using microscopy).
    \item \cite{farrell_mechanically_2013}: 2D modeling using Newtonian dynamics and only mechanical interactions + nutritient diffusion.
    Branching parameter defines diff limits where diffusion dominant and limits growth, and where it's irrelevant.
    Mechanical pressure (due to bacteria-bacteria interactions) affects growth, can limit it.(!!!)
For simulation results:
    \item \cite{farrell_mechanically_2013}: Showed the influence of mechanic interactions between bacteria in 2D system with bacteria consuming the nutritient.
    The growth of bacterial colonies where non-motile microorganisms replicate and push each other away as they grow.
    Found a transition between two different growth regimes, controlled by the balance between growth and uptake of nutrient:\\
    Exponential growth where diffusion of the nutritient does not play any role. Sublinear growth where growth is limited by nutritient diffusion.
    (Structurally in 2D it's regimes: smooth propagating of bacterial front vs. branching.)
    \item \cite{nagarajan_agent-based_2022-1}: review on the ABM for bacterial population.
    The ABM represent a microbial colony as a group of discrete agents that are governed by a set of rules, where each agent can be an individual cell or a collection of cells.
    Can use citation when talk about general processes we are accounting as growth, uptake of nutritient, production of inhibitor, e.g.,:
    Physical interactions between agents are calculated using excluded volume interactions.
    Chemical interactions as releasing inhibitors are described using concentrations and solved using PDEs.

@@

Moreover, the species 1 is able to release a certain antimicrobial component $I$ that shows inhibitory effect on species 2 (amensalism).

>>>>

% - \cite{emonet_agentcell_2005, gorochowski_bsim_2012, li_nufeb_2019, kreft_bacsim_1998}: examples of another toolboxes for bacterial communities modeling (ABM).\\
% More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.
% In general, bacterial communities in 2D can experience collective motion called swarming~\cite{wu_collective_2015}.
% Some works modelled 2D motile bacteria:
% \begin{itemize}
%     \item \cite{decoene_microscopic_2011}: 2D chemotactic self-propelled bacterial motion of the flagellated bacteria (e.g. E. coli, B. subtilis).
%     Chemotaxis here was driven by the oxygen concentrations.
%     \item \cite{rosser_modelling_2014}: modeling of the bacterial reorintation, rotation.
%     \item \cite{sokolov_physical_2012, li_amplified_2008}: modeling of the bacteria using hydrodynamic interactions and Brownian motion.
%     Fluctuations in velocity and rotations.
%     (\cite{li_amplified_2008}: Brownian motion gives right motion observed using microscopy).
%     \item \cite{farrell_mechanically_2013}: 2D modeling using Newtonian dynamics and only mechanical interactions + nutritient diffusion.
%     Branching parameter defines diff limits where diffusion dominant and limits growth, and where it's irrelevant.
%     Mechanical pressure (due to bacteria-bacteria interactions) affects growth, can limit it.(!!!)
% \end{itemize}
% For simulation results:
% \begin{itemize}
%     \item \cite{farrell_mechanically_2013}: Showed the influence of mechanic interactions between bacteria in 2D system with bacteria consuming the nutritient.
%     The growth of bacterial colonies where non-motile microorganisms replicate and push each other away as they grow.
%     Found a transition between two different growth regimes, controlled by the balance between growth and uptake of nutrient:\\
%     Exponential growth where diffusion of the nutritient does not play any role. Sublinear growth where growth is limited by nutritient diffusion.
%     (Structurally in 2D it's regimes: smooth propagating of bacterial front vs. branching.)
%     \item \cite{nagarajan_agent-based_2022-1}: review on the ABM for bacterial population.
%     The ABM represent a microbial colony as a group of discrete agents that are governed by a set of rules, where each agent can be an individual cell or a collection of cells.
%     Can use citation when talk about general processes we are accounting as growth, uptake of nutritient, production of inhibitor, e.g.,:
%     Physical interactions between agents are calculated using excluded volume interactions.
%     Chemical interactions as releasing inhibitors are described using concentrations and solved using PDEs.
% \end{itemize}

@@

Moreover, the species $A$ is able to release a certain antimicrobial component $I$ that shows inhibitory effect on species 2 (amensalism).
We assume that $L,G$ are measured in terms of overall volume and $R,I$ are measured as total amount.
